---
title: "Hw 5"
author: "Amanda Kramer"
collaborator: "Charles Biggar aka also Amanda Kramer"
note: "this is Charles Biggar's computer, so it will show him as a collaborator"
date: 11/18/20
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(readxl)
library(knitr)
library(plotly)
library(patchwork)
library(dplyr)
library("tidyr")
library("tidylog", warn.conflicts = FALSE)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```



```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```


```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  #n_unsovled
  #n_total ... 
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("./homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```




### Problem 2 
 
```{r}
set.seed(1)
file_list = list.files("./data", pattern= "*.csv")
study_data = map_df(paste("./data", file_list, sep = "/"), read_csv) %>% 
  mutate(file_name = file_list) %>% 
  separate(file_name, c("study_arm", "study_id", "csv")) %>% 
  select(study_arm, study_id, week_1:week_8, -csv) %>% 
  mutate(study_arm = ifelse(study_arm == "con", "control", "experimental"),
         study_id = c(1:20))
study_data %>% 
  pivot_longer(week_1:week_8,
    names_to = "week",
    values_to = "obs")%>% 
  ggplot(aes(x=week, y=obs, group = study_id, color = study_arm)) + geom_point() + geom_line() +
  labs(title = "Observations over time, by study arm", 
    x = "week", 
    y = "observations")
```

The control group consistantly had lower scores than the experimental group. The experimental group seemed to score higher over time, whereas the control group stayed relatively level.


## Problem 3

```{r}
sim_mean_p = function(mu) {
  
  sim_data = tibble(
    samp = rnorm(30, mean = mu, sd = 5),)
  
   t.test(pull(sim_data, samp), mu=0) %>%
      broom::tidy() %>%
      mutate(reject= (p.value < .05)) %>%
     select( estimate, p.value, reject)
}
sim_mean_p(0)
```

```{r}
sim_result = 
  tibble(mus = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = mus, ~rerun(5000, sim_mean_p(mu = .x))),
    estimates = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimates)
```
Plots

```{r}
library(plotly)
library(patchwork)


sim_result %>% 
  group_by(mus) %>%
  summarise(chance_reject = mean(reject)) %>%
  ggplot(aes(x= mus, y= chance_reject)) +
  geom_col()

avg = sim_result %>% 
  group_by(mus) %>%
  summarise(avg_mean = mean(estimate)) %>%
  ggplot(aes(x= mus, y= avg_mean)) +
  geom_col()

avg_r = sim_result %>% 
  filter(reject == TRUE) %>%
  group_by(mus) %>%
  summarise(avg_mean = mean(estimate)) %>%
  ggplot(aes(x= mus, y= avg_mean)) +
  geom_col()

avg_r + avg
```

```{r}
library(plotly)
library(patchwork)


all_data = sim_result %>% 
  group_by(mus) %>%
  ggplot(aes(x= mus, y= estimate, group = mus)) +
  geom_boxplot()

rejected = sim_result %>% 
  filter(reject == TRUE) %>%
  group_by(mus) %>%
  ggplot(aes(x= mus, y= estimate, group = mus)) +
  geom_boxplot()

all_data + rejected
```
For mus that are lower, the mean estimate of the samples that reject the null hypothesis are higher than the mean of  all the samples. The higher means are farther from 0, and therefore more likely to be rejected.


